% E. Dunham -- Resume
% Contents Copyright (C) 2014 - 2016, E. Dunham

% LaTeX code for rendering the resume is distributed under the MIT license.
% See LICENSE.txt. It means you can use the code for whatever you want,
% including your own resume, but I'm not liable if it catches your computer on
% fire.

% Template originally developed by E. Dunham
% https://github.com/edunham/resume/blob/master/resume.tex

\documentclass[11pt]{article}

% Some settings that the stuff hidden in the preamble will reference
\def \whitespaciness { 0 } % pt. bigger numbers = emptier page. 0 is ok.
\def \typeoffill {\dotfill} % hfill makes blank, dotfill makes dotted lines.


\input{preamble}
\begin{document}

\centerline{{\Huge \bf Alexander D. Anderson}}

\bigskip

\contact{alexd43anderson@gmail.com}
        {aanderson60.github.io}
        {linkedin.com/in/alexander-anderson43d/}
        {Dallas, TX}

\heading{Objective}
Research or internship position in analog electronics to apply my technical skills, tackle unique design challenges, and further my knowledge and experience in the field.

\heading{Academics}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{description}
\squish
\experience{Texas A\&M University - College Station, TX}
            {}
            {Expected 05/2023}

Bachelor of Science - Electrical Engineering, GPA: 3.86\\
Minor in Computer Science 

\end{description}

\heading{Experience}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{description}
\squish

\experience{Department of Electrical Engr., TAMU}
           {Undergraduate Researcher}
           {02/2022 - Present} 

PI: Dr. Suresh Pillai, Co-PI: Dr. Krishna Narayanan

Developed unique pooling schemes using Group Testing theory in the context of food safety.

Performed pooling experiments in a laboratory setting using Salmonella Typh.

Extensive simulation design in Python using packages including Scipy and Numpy.

\experience{Wallace Specialty Insurance Group}
           {Assistant CSR}
           {12/2018 - 08/2021}

Communicated directly with customers to solve unique problems and provide knowledge and
customer support for account issues and inquiries.

Educated and trained coworkers and new hires through workflows and tasks.

Created unique workflows and reference materials to document daily tasks and processes.

\end{description}

\heading{Skills}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\skill{Programming}
      {Python,\CPP, Java, HTML/CSS/Javascript, Verilog HDL}

\skill{Design Software}
      {LabView, SPICE, Solidworks CAD, Altium}

\skill{Lab Tools}
      {Oscilloscope, Multimeter, Soldering, Breadboarding}

\heading{Activities}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{description}
\squish
\experience{Texas A\&M Engineering Honors}
           {Member}
           {08/2019 - Present}

\experience{IEEE Texas A\&M - TEC}
           {Committee Member}
           {08/2019 - 05/2020}

Assisted in planning and executing technical workshops to educate IEEE members on hard skills
such as programming, circuit design, and microcontrollers.

Managed team of students in planning and building a drone.

\experience{TAMUHack 2022}
           {Best Novice Hack}
           {01/2022}

Worked collaboratively in a group to develop project \emph{myMirror}, a smart mirror featuring
Google Calendar integration and live weather data.

https://devpost.com/software/mymirror

\end{description}

\heading{Honors}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{description}
\squish
\experience{Eagle Scout}
           {Boy Scouts of America}
           {12/2016}

Highest distinction in the Boy Scouts of America earned by directly demonstrating
leadership, service, and knowledge in various categories.

\experience{McFadden Scholarship}
           {Texas A\&M University}
           {08/2019}

4-year scholarship based on exceptional academic achievement, leadership, and extracurricular activities.

\experience{Dean's Honor Roll}
           {College of Engineering}
           {05/2020, 12/2020}

\end{description}

\end{document}
